---
title: "Peer-graded Assignment 1: R Markdown and Leaflet"
author: "Anastasia Simmet (geb. Morozova)"  
date: "January 30, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This R Markdown document features a map created with Leaflet. This map marks the places that are precious to me. There are four cities that I consider home. These cities are marked with the circle markers on the map. The size of the markers represents how many years I lived in a particular city and the color represents the stage of my life. :) In the popup of every marker you can see the Coat of arms of a particular city, the name of the city with the link to the Wikipedia article about this city. Enjoy! 

## The MAP

```{r eruptions, echo=FALSE, message=FALSE}
library(leaflet)

# dataframe with cities
cities <- data.frame(name = c("Nadym", "Moscow", "Konstanz", "Wangen im Allgäu"),
                        years = c(18, 5, 3, 1),
                        col = c("red", "blue","blue", "green" ),
                        lat = c(65.53333,  55.751244, 47.6744, 47.6939),
                        lng = c(72.51667, 37.618423, 9.1649, 9.829))

# define the links to the Wikipedia pages related to the cities
wiki<-c(
  "<a href='https://en.wikipedia.org/wiki/Nadym'>Nadym</a>",
  "<a href='https://en.wikipedia.org/wiki/Moscow'>Moscow</a>",
  "<a href='https://de.wikipedia.org/wiki/Konstanz'>Konstanz</a>",
  "<a href='https://en.wikipedia.org/wiki/Wangen_im_Allg%C3%A4u'>Wangen im Allgäu</a>"
)

# URLs with images of the Coats of arms
file1<-'https://upload.wikimedia.org/wikipedia/commons/c/c5/Coat_of_Arms_of_Nadym_and_Nadymsky_rayon_%28Yamal_Nenetsia%29.png'
file2<-'https://upload.wikimedia.org/wikipedia/commons/thumb/b/bb/Coat_of_Arms_of_Moscow.svg/800px-Coat_of_Arms_of_Moscow.svg.png'
file3<-'https://upload.wikimedia.org/wikipedia/commons/thumb/8/8f/Wappen_Konstanz.svg/800px-Wappen_Konstanz.svg.png'
file4<-'https://upload.wikimedia.org/wikipedia/commons/thumb/d/d0/Wappen_Wangen_im_Allg%C3%A4u.svg/800px-Wappen_Wangen_im_Allg%C3%A4u.svg.png'

# Creating the map
cities %>%
  leaflet() %>%
  addTiles() %>%
  addCircleMarkers(weight = 1, radius = sqrt(cities$years)*4,color = cities$col, popup = paste0(wiki, "<img src = ", c(file1,file2,file3,file4), ">")) %>%
  addLegend(labels = c("Childhood","Study","Work"), colors = c("red", "blue","green"))
```
