---
title: "Exploratory graphs with Plotly"
author: "Anastasia Simmet (geb. Morozova)"
date: "6 February 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

This presentation features creation of the interactive plots using Plotly as a part of the exploratory data analysis of the dataset **ToothGrowth** in R.  

## Procedures to be done

- We load the library with the dataset of interest using the following command 
```{r, echo = TRUE, eval=FALSE, message=FALSE}
library(datasets)
data(ToothGrowth)
```
- We look into the structure of the dataset
```{r, echo = TRUE, eval=FALSE, message=FALSE}
library(dplyr)
str(ToothGrowth)
ToothGrowth$dose<-as.factor(ToothGrowth$dose)
summary(ToothGrowth)
```
##
- We use Plotly to perform exploratory data analysis
```{r, echo = TRUE, eval=FALSE, message=FALSE}
library(plotly)
# histogram of the tooth length
plot_ly(x=ToothGrowth$len, type="histogram")
# boxplots of the tooth length by the type of supplements
plot1<-ggplot(data=ToothGrowth,aes(x = supp, y = len))+
      geom_boxplot(aes(fill=supp))
(gg<-ggplotly(plot1))
# boxplots of the tooth length by the type of supplements and the dose
plot2<-ggplot(data=ToothGrowth,aes(x = supp, y = len))+
      geom_boxplot(aes(fill=supp)) + facet_wrap(~ dose)
(gg<-ggplotly(plot2))
```
## Structure of the dataset
```{r, echo = TRUE, message=FALSE}
library(dplyr)
str(ToothGrowth)
ToothGrowth$dose<-as.factor(ToothGrowth$dose)
summary(ToothGrowth)
```

## The histogram 
```{r, echo = TRUE, message=FALSE}
library(plotly)
# histogram of the tooth length
plot_ly(x=ToothGrowth$len, type="histogram")
```

## The boxplot by the type of supplement 
```{r, echo = FALSE, message=FALSE}
library(plotly)
# boxplots of the tooth length by the type of supplements
plot1<-ggplot(data=ToothGrowth,aes(x = supp, y = len))+
      geom_boxplot(aes(fill=supp))
(gg<-ggplotly(plot1))
```

## The boxplot by the type of supplement and the dose
```{r, echo = FALSE, message=FALSE}
library(plotly)
# boxplots of the tooth length by the type of supplements and the dose
plot2<-ggplot(data=ToothGrowth,aes(x = supp, y = len))+
      geom_boxplot(aes(fill=supp)) + facet_wrap(~ dose)
(gg<-ggplotly(plot2))
```

##

Thank you for the review!



